A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-21 writeup/paper.tex
Additional questions that we could address

>>>>

Other questions:
\begin{itemize}
\item Are Turkers cheating by using Google translate?  Is there a difference in their use of MT systems for Latin alphabet languages v. languages with scripts that are more difficult to type?
\item Are there flaws in our gold standard translations?  Are they too easy because they've already been indexed by Google?  Are they too hard for some languages because they are obscure scientific terms?
\item Can we select good gold standard translations for future studies?  Which translations are we confident in?
\item How well do the Turker translations match external bilingual dictionaries?  If we ranked Turkers by how well they performed on our controls, would those rankings stay stable if we ranked them based on their performance on external dictionaries? 
\item How well do Turkers agree with each other on non-control items?  Should we run a synonym HIT on all of the non-identical translations?  Would that help us understand which translations were good and which weren't?  
\end{itemize}
